% LaTeX set-up adapted from a template by Alan T. Sherman (9/9/98)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\input{/home/anton/Documents/latex/LaTeXHeader.tex} % put hard path to header.
\usepackage{soul}
\usepackage{hyperref}
\allowdisplaybreaks

%%%%%% Begin document with header and title %%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\mymascheader
\pagestyle{plain}
{\begin{center} {\large {\bf Statistical Arbitrage with \\  Limit Order Book Imbalance}} \end{center}}
\bigskip

%%%%% Begin body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{quote}
My goal is to establish and solve the stochastic optimal control problem that 
captures the momentum and order imbalance dynamics of the Limit Order Book 
(LOB). The solution will yield an optimal trading strategy that will permit
statistical arbitrage of the underlying stock, which will then be backtested on
historical data.
\end{quote}

\section*{Progress Timeline}
\vspace{-10pt}
\begin{table}[H]
\renewcommand\arraystretch{1.4}\arrayrulecolor{LightSteelBlue3}
\newcommand{\foo}{\color{LightSteelBlue3}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\newcommand{\fooo}{\color{LightSteelBlue3}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
\begin{tabular}{@{\,}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash}p{9cm} !{\fooo} >{\raggedright\arraybackslash}p{5cm}} 
\multicolumn{1}{@{\,}r <{\hskip 9pt}}{DATE} & \multicolumn{1}{l}{THESIS} & \multicolumn{1}{l}{STA4505} \\
\hline
\st{Dec 2014} & \st{Complete CTMC calibration} \\
\st{Dec 2014} & \st{Backtest naive strategies based on CTMC} & \\
\st{Jan-May} & \st{Study stochastic controls: ECE1639, STA4505} & \\
\st{Jun 5} & \st{Establish models} & \st{Exam Study} \\
\st{Jun 12} & \st{Establish performance criteria} & \st{Exam Study} \\
\st{Jun 15} & \st{Derive DPP/DPE} & \st{EXAM} \\
\st{Jun 26} & \st{Derive continuous-time equations} & \\
\st{Jul 3} & \st{Derive discrete-time equations} & \\
\st{Jul 10} & \st{Set up MATLAB numerical integration} &  \\
\st{Jul 17} & \st{Integrate functions and plot dynamics} & \st{Integrate and analyze} \\
\st{Jul 24} & \st{Empty promises; zero fucks given} & \\
\st{Jul 31} & \st{Code for numerical solutions, calibrations, plots} & \st{Simulate results} \\
\st{Aug 7} & \st{All in-sample backtests} & \\
\st{Aug 14} & \st{All out-of-sample backtests} & \\
Aug 21 & The Big Writeup Effort & \\
{\bf Aug 24} & {\bf Submit first draft for review by panel} & \\
Aug 28 & & Project Report \\
Sep 2 & & Presentation
\end{tabular}
\end{table}

\newpage
\section*{Whiteboard Inspirational Quote of the Week}

\section*{For Our Colleagues at Duke University...}

\clearpage 
\section*{The Academic Week in Review}
\begin{itemize}[topsep=0pt,itemsep=0ex,partopsep=0ex,parsep=0ex]
\item out-of-sample backtest: 2014 data.
\begin{itemize}[topsep=0pt,itemsep=0ex,partopsep=0ex,parsep=0ex]
\item \st{decide WHAT to run. best performer? probably annual calib is easiest, tho. justify. also consider expanding the finite differences horizon $T$ for more accurate results...}
\item \st{run backtest. ~0.5h per strategy.}
\item print results table
\item plot EOD results
\item writeup
\end{itemize}

\item Dynamics of $\delta^\pm$ for continuous vs discrete time
\begin{itemize}[topsep=0pt,itemsep=0ex,partopsep=0ex,parsep=0ex]
\item \st{produce plots comparing for different q,z values.}
\item \st{mimic Seb's four plots to show mechanics of the FOUR methods}
\item writeup something intelligible about the plots
\end{itemize}

\item General writing stuff
\begin{itemize}[topsep=0pt,itemsep=0ex,partopsep=0ex,parsep=0ex]
\item \st{write introduction}
\item \st{write algo trading section}
\item \st{write LOB dynamics section}
\item write intro to stochastic chapter
\item Link STA4505 project into dissertation with lead-in blurb.
\item re-write lead-in to continuous time section
\item re-write lead-in to discrete time section
\item write conclusion chapter
\item write ITCH data section
\item write abstract
\end{itemize}

\item any remaining time to proof-read the bitch
\item {\bf SUBMIT THE BITCH}
\item write acknowledgement
\item write dedication
\item STA4505 project standalone write-up.
\end{itemize}

\end{document}