% system description - each variable.
\begin{frame}
\frametitle{System Description}
\begin{itemize}
\item Imbalance Averaging Time $\Delta {t_{I}}$ \\
    A constant, specifying the time window over which the imbalance ratio $I(t)$ will be averaged.
\item Price Change Time $\Delta {t_{S}}$ \\
    A constant, specifying the time window over which price changes will be computed.
\item Number of Imbalance Bins $\#_{bins}$ \\ 
    A constant, specifying the number of bins (spaced by percentiles, symmetric around zero) into which $I(t)$ will be sorted.
\item Imbalance $\rho_t$ \\
    The finite, discrete stochastic process that results from sorting $I(t)$ into the imbalance bins $\{1, \dots, \#_{bins} \}$, and which evolves in accordance with the CTMC $\bZ$.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{System Description}
\begin{itemize}
\item Midprice $S_t$ \\
    Stochastic process, evolves according to CTMC $\bZ$.
\item Midprice Change $\Delta S_t = \sgn(S_t - S_{t-\Delta {t_{S}}})$
\item Imbalance \& Midprice Change $\bZ_t = (\rho_t, \Delta S_t) $ \\
    Continuous-time Markov chain with generator $\mat{G}$.
\item Bid-Ask Half-Spread $\xi$ \\
    Assumed constant. $2\xi$ is equal to the bid-ask spread.
\item Midprice Change $\{ \eta_{0,\bz}, \eta_{1,\bz}, \dots \} \sim F_{\bz}$ \\
    i.i.d. RVs, with distribution dependent on the Markov chain state.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{System Description}
\begin{itemize}
\item Other Agent Market Orders $K^{\pm}_t$ \\
    Poisson processes with rate $\mu^{\pm}(\bZ_t)$. $K^+$ represents the arrival of another agent's buy market order.
\item Our Limit Order Posting Depth $\delta^{\pm}_t$ \\
    One of our controlled $\cF$-predictable processes. $\delta^+$ dictates how deep on the buy side we will post our buy limit order; $\delta^+ = 0$ implies at-the-touch.
\item Our Limit Order Fill Count $L^{\pm}_t$ \\
    Counting processes (not Poisson), satisfying
    \[ \P [\d L^{\pm}_t = 1 \, | \, \d K^{\mp}_t = 1] = e^{-\kappa \delta^{\pm}_t} \]
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{System Description}
\begin{itemize}
\item Fill Probability Constant $\kappa$ \\
    Fitted to satisfy the above relation, by considering the avg vol available at the first few depths relative to distribution of volumes of incoming market orders
\item Our Market Orders $M^{\pm}_t$ \\
    $M^+$ represents our buy market order. Assume we achieve the best bid/ask price.
\item Our Market Order Execution Times $\btau^\pm = \{ \tau^\pm_k : k = 1, \dots \}$ \\
    An increasing sequence of $\cF$-stopping times.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{System Description}
\begin{itemize}
\item Cash $X^{\btau, \delta}_t$ \\
    A stochastic variable representing our cash, initially zero, that evolves according to
\[ \begin{aligned}
\d X^{\btau, \delta}_t = & \underbrace{(S_t + \xi + \delta^{-}_t) \d L^{-}_t}_{\text{sell limit order}} - \underbrace{(S_t - \xi - \delta^{+}_t) \d L^{+}_t}_{\text{buy limit order}} \\
                         & + \underbrace{(S_t - \xi) \d M^{-}_t}_{\text{sell market order}} - \underbrace{(S_t + \xi) \d M^{+}_t}_{\text{buy market order}}
\end{aligned} \]
\item Inventory $Q^{\btau, \delta}_t$ \\
    A stochastic process representing our assets, initially zero, that satisfies
\[ Q^{\btau, \delta}_0 = 0, \qquad Q^{\btau, \delta}_t = L^+_t + M^+_t - L^-_t - M^-_t \]
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Terminal Wealth}
Call $W^{\btau, \delta}_t$ our net present value (NPV) at time $t$.
Hence $W^{\btau, \delta}_T$ at terminal time $T$ is our `terminal wealth.' 

At $T$, we:
\begin{itemize}
\item finish each trading day with zero inventory (avoid overnight positional risk)
\item submit a market order (of a possibly large volume) to liquidate remaining stock
\item price achieved will be $S - \xi \sgn Q - \alpha Q$
\begin{itemize}
\item $\xi \sgn Q$ represents crossing the spread
\item $\alpha$ is a penalty constant
\item $\alpha Q$ represents receiving a worse price linearly in $Q$ due to walking the book
\end{itemize}
\end{itemize}

Hence, $W^{\btau, \delta}_t$ satisfies:
\[
W^{\btau, \delta}_t = \underbrace{\vphantom{\left( Q^{\btau, \delta}_t) \right)}X^{\btau, \delta}_t}_{\text{cash}}+ \underbrace{Q^{\btau, \delta}_t \left( S_t - \xi \sgn(Q^{\btau, \delta}_t) \right)}_{\text{book value of assets}} - \underbrace{\alpha \left( Q^{\btau, \delta}_t \right)^2}_{\text{liquidation penalty}}
\]
\end{frame}

% perf crit and value func
\begin{frame}
\frametitle{Dynamic Programming Value Function}
Our performance criterion will be to maximize terminal wealth:
\[
H^{\btau, \delta}(t,x,s,\bz,q) = \E_{t,x,s,z,q} \left[ W_T^{\btau, \delta} \right]\vphantom{\int\limits_t^T}
\]

The \emph{value function} is given by
\[
H(t,x,s,\bz,q) = \sup\limits_{\btau \in \mathcal{T}_{[t,T]}} \sup\limits_{\delta \in \cA_{[t,T]}} H^{\btau, \delta}(t,x,s,\bz,q)
\]

Admissible trading strategies is the product of the set $\mathcal{T}$ of all $\cF$-stopping times, with the set $\cA$ of all $\cF$-predictable, bounded-from-below depths $\delta \geq 0$.
\begin{itemize}
\item recognizing $\tau$ does not require knowledge of the future
\item $\delta$ cannot `see into the future'; measurable with respect to information at an earlier time
\end{itemize}
\end{frame}

% solve dH...
\begin{frame}
\frametitle{}
\end{frame}

% comp proc for Markov chain
\begin{frame}
\frametitle{}
\end{frame}

% inf gen
\begin{frame}
\frametitle{}
\end{frame}

% resulting DPE w/ bdry cond
\begin{frame}
\frametitle{}
\end{frame}

% ansatz
\begin{frame}
\frametitle{}
\end{frame}

% simplified inf gen with sgn
\begin{frame}
\frametitle{}
\end{frame}

% opt posting d+ and floored d+
\begin{frame}
\frametitle{}
\end{frame}

% final DPE
\begin{frame}
\frametitle{}
\end{frame}

%%% INTERPRET DPE
% MO conditions
\begin{frame}
\frametitle{}
\end{frame}

% continuation region conditions
\begin{frame}
\frametitle{}
\end{frame}

% bounds on d+/-
\begin{frame}
\frametitle{}
\end{frame}