% ************************** Thesis Acknowledgements **************************
\newenvironment{acknowledgements}%
	{\cleardoublepage\thispagestyle{empty}%
	\chapter*{\centering \Large Acknowledgements}}%
	
	\begin{acknowledgements}
I couldn't begin to enumerate the times and ways this dissertation could have failed to be. I am deeply grateful to several individuals for making it a reality, and I'd like to acknowledge them here.

\href{http://www.sr.utias.utoronto.ca/}{\bf Dr. Gabriele D'Eleuterio}, my supervisor at UTIAS, is the epitomical supernatural mentor of the hero journey, without whom I would have abandoned my studies. Gabe was the inspirational upholder of academic values, who relentlessly stressed the subtleties of scientific presentation and communication, and guided me through a pretty tough time. Thank you for your support, guidance, and for every coffee.

\href{http://www.utstat.utoronto.ca/sjaimung/}{\bf Dr. Sebastian Jaimungal}, professor of statistics at the university, took me on as a surrogate student half-way through my studies, and guided every step of this dissertation. Despite having absolutely no obligation to do so, he had faith in me and patience with me in navigating an entirely unfamiliar subject. Thank you for repeatedly making yourself available to help with all the math.

\href{http://jackcarlyle.co.uk/}{\bf Dr. Jack Carlyle}, then a PhD student in solar physics at UCL, inspired me to quit my job and go back to school for a graduate degree. It wasn't an easy decision, and the jury is out on whether it was a good one. But thanks for all the tea and crumpets.

\href{https://www.linkedin.com/in/tedherman}{\bf Ted Herman}, a friend that redefines friendship, has read more of my research than anyone ever will. At a crucial time, we struck the \href{http://www.fransrestaurant.com/home}{Fran's} Accord that involved prewritten \$100 cheques being shredded on a weekly basis upon receipt of a progress update. Legitimately, this is probably the number one reason that my dissertation got done.

Thank you {\bf mom} for always loving, supporting, and inspiring me to my best. Thank you {\bf dad} for pretty well being a supervisor too.
	\end{acknowledgements}